Choices with the group_by and summarize functions

### 2025-02-11 text/25/group-by-choices.Rmd
Added links to group-by-choices

---
title: "New RMarkdown program"
author: "Steve Simon"
source: new
date: "2025-02-11"
categories:
- Blog post
tags:
- R programming
output: html_document
page_update: complete
---

You have an interesting choice in an R program When you use the group_by function with two or more arguments and follow that with the summarize function. Here is a practical illustration of how your choices.

@@

>>>>

---
title: "Choices with the group_by and summarize functions"
author: "Steve Simon"
source: new
date: "2025-02-11"
categories:
- Blog post
tags:
- R programming
output: html_document
page_update: complete
---

You have an interesting choice in an R program When you use the group_by function with two or more arguments and follow that with the summarize function. Here is a practical illustration of how your choices can make a difference.

@@

## More information

Like most of the tidyverse documentation, the information on summarize is very complete. Sometimes so complete as to be overwhelming. Look first at the summarise section in the [vignette on grouping][ref01]. The [documentation page on count][ref02] does not go into detail about the inconsistency between the count function and the group_by followed by summary functions, but is still worth reading.

[ref01]: https://dplyr.tidyverse.org/articles/grouping.html#summarise
[ref02]: https://dplyr.tidyverse.org/reference/count.html
